---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "Readme_files/"
)
```

# DataSHIELD Use-case

This repository contains a short use-case base on the three packages `ds.predict.base`, `ds.calibration`, and `ds.roc.glm`. The main intend is to have a short script which can be used for testing the functionality of these packages.

The following contains the script for the use-case as well as the output.

## DataSHIELD Setup

Install all packages locally and also on the DataSHIELD test machine. Also fit a logistic regression, create a new project and upload the data sets:

```{r}
remotes::install_github("difuture-lmu/ds.predict.base")
remotes::install_github("difuture-lmu/ds.calibration")
remotes::install_github("difuture-lmu/ds.roc.glm")

source(here::here("R/update-data.R"))
source(here::here("R/upload-data.R"))
source(here::here("R/create-log-reg.R"))
source(here::here("R/install-ds-packages.R"))
source(here::here("R/helper.R"))
```

## Log into DataSHIELD server

```{r}
library(DSI)
library(DSOpal)
library(dsBaseClient)

library(ds.predict.base)
library(ds.calibration)
library(ds.roc.glm)

builder = newDSLoginBuilder()

surl     = "https://opal-demo.obiba.org/"
username = "administrator"
password = "password"

datasets = c("KUM", "MRI", "UKA", "UKT")
for (i in seq_along(datasets)) {
  builder$append(
    server   = paste0("ds", i),
    url      = surl,
    user     = username,
    password = password,
    table    = paste0("DIFUTURE-TEST.", datasets[i])
  )
}

## Get data of the servers:
conn = datashield.login(logins = builder$build(), assign = TRUE)
datashield.symbols(conn)
```

## Push and predict

```{r}
## Load the pre-calculated logistic regression:
load(here::here("data/mod.Rda"))

## Push the model to the servers:
pushObject(conn, obj = mod)
datashield.symbols(conn)

## Predict the model on the data sets located at the servers:
predictModel(conn, mod, "pred", predict_fun = "predict(mod, newdata = D, type = 'response')")
datashield.symbols(conn)
```

## Analyse calibration of the predictions

```{r}
brier = dsBrierScore(conn, "D$binomial_1", "pred")
brier
cc = dsCalibrationCurve(conn, "D$binomial_1", "pred")
plotCalibrationCurve(cc, size = 1.5)
```

## Evaluate the model using ROC analysis

```{r}
roc_glm = dsROCGLM(conn, "D$binomial_1", "pred", lag = 1, ntimes = 1)
plot(roc_glm) + ggplot2::theme_minimal()
```

## Cross check on pooled data:

```{r}
## Check on pooled data:
library(mlr)
load(here::here("data/dat_full.Rda"))

task = makeClassifTask(data = dat, target = "binomial_1")
lrn  = makeLearner("classif.logreg", predict.type = "prob")
mod  = train(lrn, task)
pred = predict(mod, task = task)

auc_pooled   = measureAUC(pred$data$prob.1, pred$data$truth, negative = 0, positive = 1)
brier_pooled = measureBrier(pred$data$prob.1, pred$data$truth, negative = 0, positive = 1)

df = generateThreshVsPerfData(pred, measure = list(fpr, tpr))

gg_roc_glm = plot(roc_glm)
gg_roc_glm +
  ggplot2::geom_line(data = df$data, ggplot2::aes(x = fpr, y = tpr), color = "dark red", alpha = 0.6) +
  ggplot2::theme_minimal()

var_auc = deLongVar(pred$data$prob.1, pred$data$truth)
ci = logitToAUC(pepeCI(toLogit(auc_pooled), 0.05, var_auc))

cross_check = data.frame(
  "Distributed Data" = c(brier, roc_glm$auc, roc_glm$ci[1], roc_glm$ci[2]),
  "Pooled Data" = c(brier_pooled, auc_pooled, ci[1], ci[2]))
rownames(cross_check) = c("Brier Score", "AUC", "CI(0.95) (lower)", "CI(0.95) (upper)")
knitr::kable(cross_check)
```

## Log out from DataSHIELD servers

```{r}
datashield.logout(conn)
```
